---
title: "p8105_hw6_yh3822"
output: github_document
date: "2024-12-01"
---

```{r set up}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(tidyverse)
library(dplyr)
library(broom)
library(p8105.datasets)

set.seed(1)
```



```{r, warning=FALSE, message=FALSE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```



## Problem 1


```{r}
bootstrap_analysis = function(data) {
  model = lm(tmax ~ tmin, data = data)
  r_squared = glance(model)$r.squared
  coefs = tidy(model)
  log_beta0_beta1 = log(coefs$estimate[1] * coefs$estimate[2])
  
  tibble(
    r_squared = r_squared,
    log_beta0_beta1 = log_beta0_beta1
  )
}
```



```{r}
bootstrap_results = weather_df |>
  modelr::bootstrap(n = 5000) |> 
  mutate(results = map(strap, ~ bootstrap_analysis(as_tibble(.)))) |> 
  select(results) |> 
  unnest(results)
```



```{r}
bootstrap_results %>%
  ggplot(aes(x = r_squared)) +
  geom_density(fill = "blue", alpha = 0.5) +
  labs(title = "Distribution of R-squared", x = "R-squared", y = "Density")
```

This plot shows that the model consistently explains a high proportion of the variance in values primarily ranging between 0.88 and 0.94, and the density plot of r_squared is approximately symmetric.



```{r}
bootstrap_results %>%
  ggplot(aes(x = log_beta0_beta1)) +
  geom_density(fill = "green", alpha = 0.5) +
  labs(title = "Distribution of log(beta0 * beta1)", x = "log(beta0 * beta1)", y = "Density")
```


The distribution is symmetric, indicating consistent estimates across bootstrap samples and minimal variability in log(beta0*beta1). It suggests a stable relationship between tmax and tmin.


```{r}
bootstrap_results %>%
  summarise(
    r_squared_lower = quantile(r_squared, 0.025),
    r_squared_upper = quantile(r_squared, 0.975),
    log_beta0_beta1_lower = quantile(log_beta0_beta1, 0.025),
    log_beta0_beta1_upper = quantile(log_beta0_beta1, 0.975)
  )
```



## Problem 2


```{r}
homicide_df = read_csv("./data/homicide-data.csv") |>
  mutate(
    city_state = paste(city, state, sep = ", "),
    solved = if_else(disposition == "Closed by arrest", 1, 0),
    victim_age = as.numeric(victim_age)
  ) |>
  filter(
    !city_state %in% c("Dallas, TX", "Phoenix, AZ", "Kansas City, MO", "Tulsa, AL"),
    victim_race %in% c("White", "Black"),
    !is.na(victim_age)
  )
```


```{r}
baltimore_data = homicide_df |>
  filter(city_state == "Baltimore, MD") 

baltimore_model =
  glm(solved ~ victim_age + victim_sex + victim_race, data = baltimore_data, family = "binomial")
```


```{r}
baltimore_model %>%
  broom::tidy() %>%
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>%
  filter(term == "victim_sexMale")
```



```{r}
homicide_df |>
  group_by(city_state) |>
  nest() |>
  mutate(
    glm_model = map(data, ~ glm(solved ~ victim_age + victim_sex + victim_race, 
                                data = ., family = "binomial")),
    glm_tidy = map(glm_model, ~ broom::tidy(.) |>
                     mutate(
                       OR = exp(estimate),
                       CI_lower = exp(estimate - 1.96 * std.error),
                       CI_upper = exp(estimate + 1.96 * std.error)
                     ) |>
                     filter(term == "victim_sexMale"))
  ) |>
  unnest(glm_tidy) |>
  select(city_state, OR, CI_lower, CI_upper)
```


```{r}
city_results = homicide_df |>
  group_by(city_state) |>
  nest() |>
  mutate(
    glm_model = map(data, ~ glm(solved ~ victim_age + victim_sex + victim_race, 
                                data = ., family = "binomial")),
    glm_tidy = map(glm_model, ~ broom::tidy(.) |>
                     mutate(
                       OR = exp(estimate),
                       CI_lower = exp(estimate - 1.96 * std.error),
                       CI_upper = exp(estimate + 1.96 * std.error)
                     ) |>
                     filter(term == "victim_sexMale"))
  ) |>
  unnest(glm_tidy) |>
  select(city_state, OR, CI_lower, CI_upper)

city_results= city_results|>
  arrange(OR) |>
  mutate(city_state = factor(city_state, levels = city_state)) 
  
ggplot(data = city_results, aes(x = city_state, y = OR)) +
  geom_point() +
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper), width = 0.2) +
  coord_flip() +
  labs(
    title = "Adjusted Odds Ratios for Solving Homicides by City",
    x = "City",
    y = "Odds Ratio"
  ) +
  theme_minimal()
```


The majority of cities have ORs near 1, suggesting that gender does not strongly influence the likelihood of solving homicides. A few cities show ORs significantly greater or less than 1. Some cities have wide confidence intervals, indicating less certainty in the OR estimates.









